\section{Introduction}
\subsection{IlliniSat}
A CubeSat is a small satellite ($\sim$~1kg) built usually out of commercial components
that is used for scientific research. It can be delivered as a secondary payload or 
as a ``shared ride'' with a number of other satellites to decrease costs.
\cite{toorian2008cubesat}.  
With an estimated cost of roughly
\$52,000\footnote{\url{http://www.satmagazine.com/story.php?number=602922274}}
to put an educational CubeSat in orbit, CubeSats are well within the budget of
many universities.  The University of Illinois has a
CubeSat\footnote{\url{http://cubesat.ae.illinois.edu/index.php}} program in
which a class and dedicated team have been developing a scalable picosatellite
($<$~1kg) bus, IlliniSat-2.  IlliniSat-2 is intended to be used for multiple
missions, the first of which (Lower Atmosphere/Ionosphere Coupling Experiment,
LAICE) is planned to launch around December 2014.  This mission will involve
three scientific payloads: one from Illinois and two from Virginia Tech.  In
collaboration with Bindu Jagannatha and Alex Ghosh of the IlliniSat-2 team, this
project aims to analyze and enhance the reliability of the computing systems
used in IlliniSat-2.

The IlliniSat-2 bus contains various systems, and this project focuses on the
Command and Data Handling (C\&DH) system.  The C\&DH system is responsible
for maintaining the mission schedule and coordinating the communication of the
satellite with the ground station.  The C\&DH system is based on a MitySOM-335x
Processor Card, built with a TI AM335x Application Processor System-on-Chip
(SoC).\footnote{\url{http://www.criticallink.com/wp-content/uploads/MitySOM-335x_Datasheet.pdf}}
An embedded Linux distribution, Arago, is run on top of the TI SoC and
IlliniSat's functionality is implemented in set of userspace daemons. The
standard \fix{atd} utility is used to schedule tasks.
%FIXME: include C&DH figure 

Currently, the system has a watchdog timer that will reboot the flight computer
if it does not receive a heartbeat every 60 seconds.  The watchdog is part of a
health monitoring system that also observes the state of the battery, satellite 
attitude, temperature, etc. If the health monitor determines that the system
is in a faulty state, it will transition C\&DH into a recovery mode (e.g. if the
battery is low, switch off all nonessentials and point the satellite towards the
sun).
%FIXME: do we want the health monitor figure?
%FIXME: define SPoF

\subsection{Design Constraints}
The IlliniSat bus has many hardware and software requirements that constrain our
improvements of the system. Since the IlliniSat team has already chosen their
hardware, we will have to make all of our changes in software. Given the nature
of the mission, the software is required to have mission critical components
that cannot fail. The main design constraints that will be put on us while improving the system are the following:
\begin{itemize}
  \item Preserve real-time deadlines
  \item Minimize additional power consumption
  \item Avoid complex solutions
\end{itemize}
IlliniSat needs to be constantly reacting to its environment so that it can
interface with payloads, communicate to the ground, and monitor the health of
the system, among other things. Because of this, hard real-time deadlines are
required and cannot be missed. 

Since IlliniSat is such a small satellite with stringent physical dimensions and
therefore limited battery capacity, power is a major concern for the team.  If
too much power is consumed, the battery may not last while the satellite is not
receiving solar power (if it is either eclipsed by the earth or positioned
poorly).  Also, if the system is charging and the CPU is loaded, components may
start to overheat.  Any software reliability techniques used should therefore be
mindful not to use too much power and should also be aware of the current state
of the satellite (recovery modes, etc...).

Finally, the IlliniSat team has requested that we keep our solution simple (and
well documented) so that it can be implemented and maintained easily.
Furthermore, we need to be careful not to implement overly intricate solutions
that may introduce new failure modes or reduce the system's reliability.
