\section{Proposed Approach}
\subsection{M\"obius simulation of memory corruption}
In order to provide the IlliniSat team with useful data about the reliability of
the satellite, we intend to develop simulations in M\"obius to indicate the
potential for failures due to flash corruption during the 6 month - 1 year
mission time frame.  As IlliniSat must store data it collects from experiments
before transmitting it to the ground station, the probability that an arbitrary
flash error corrupts existing data increases the longer the satellite goes
without communicating with the ground station.  Furthermore, the Operating
System and user programs are stored in flash memory and these are all necessary
for proper operation of the satellite.  We intend to evaluate the IlliniSat's
performance in both the presence and the absence of detection provided by the flash patrol read daemon discussed below and an ideal recovery system that is able to correct all detected errors.

\subsection{Develop a consistent boot/recovery procedure}
When the project members were conversing with the IlliniSat team, one major
concern that the IlliniSat team had was that the system may not boot up
correctly after the watchdog resets the system (or even after deployment).  This
can happen for a number of reasons, but one of the main concerns is corruption
of the Operating System kernel image stored in flash memory.  If the OS kernel
does not boot, this mission will end in catastrophic failure as all systems run
on top of the OS.  One idea to address this is to store multiple copies of the
OS kernel, along a checksum for the kernel image.  When booting a kernel, the
bootloader can compute the checksum at boot time and failover to the next kernel
image if it does not match the stored checksum.  While this removes the stored
kernel image as a SPoF, it still leaves the bootloader as a SPoF.  However, the
bootloader's code is significantly smaller than the Linux kernel and therefore
should be less susceptible to bit errors.  If time permits, we can investigate
similar techniques for protecting the bootloader. 

\subsection{Develop a flash patrol read daemon}
In addition to storing the Operating System and programs, IlliniSat uses flash
memory to store up to 30 days of scientific data before it can be transmitted to
the ground station.  To ensure that the data is not corrupted, we plan to
implement a flash patrol read daemon that will sweep over the flash memory and
validate the contents. We plan to do this using a checksum or possibly even an
in memory cache (if storage space permits).  Storing the detection data in
memory allows us to take advantage of the fact that DRAM is more reliable than
flash memory in CubeSats~\cite{odegaard2013error}.  The patrol will run in the
background to make certain that it does not interfere with the real-time
deadlines that are mission critical.  In addition, the patrol will be
implemented such that it checks the flash that is being used instead of just
iterating through its entirety (e.g.  data that has already been transmitted
will no longer be validated). With regards to power consumption, we can ensure
that the daemon only runs while the satellite has sufficient power remaining.
Adding the patrol daemon to the IlliniSat system will help safeguard that no
data is lost on the satellite, allowing its scientific missions to be
successful.

\subsection{Develop a method to increase reliability of ground station
communications}
The ground station is able to send commands from the ground to IlliniSat. These commands
can change the state of the satellite and also the configuration settings. This makes sense because the
researchers on the ground may want to update the mission objectives or fix new bugs. However, this
means that the ground station has a large amount of control over the
satellite. If the commands were somehow corrupted in transit,
the satellite could be sent into an unknown state with unknown settings. 
It is then possible that the satellite could keep restarting, hang, or just crash altogether. All of these are
unacceptable failures and must be avoided. So we plan to develop a system of validating the 
communications that are sent from the ground before actually interpreting them. This method could 
involve a checksum or even a fixed set of commands that are stored on the satellite and then indexed 
by the commands sent from the ground. Ensuring the correctness of these commands
will can help guarantee a stable state
on the satellite and thwart transient errors.
